\documentclass[12pt,a4paper]{report}
\usepackage[utf8]{inputenc}
\usepackage{textcomp}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{color}
\usepackage{graphicx}
\usepackage{anysize}
\marginsize{2cm}{2cm}{1cm}{3cm} %left, right, top, bot margin
\usepackage{enumitem}

\title{Requirements}
\author{Jacob Kristensen\\Morten Bøndinge Koch\\Anders Bech\\ Henrik Holm Christensen\\EDE - Electronic Design Engineer\\AU-Herning\\}
\date{17/02-12}



\begin{document}

\chapter{requirements}
Below all the requirements are listed. They are divided into four major categories; Functional, non-functional, behavioural and performance requirements. They are derived from our customer needs / customer requirements.\\
They are further divided into smaller groups, describing the category, could be safety, environmental etc.. First Below there is an example of how requirements are referred to throughout this report:\\

Functional Requirements [FR]
\begin{enumerate}
\item Safety [FR.1]
\begin{enumerate}
	\item The system shall be safe. [FR.1.a]
	\begin{enumerate}
		\item Very safe. [FR.1.a.i]
	\end{enumerate}
\end{enumerate}
\end{enumerate}
CR - Customer Requirements (Needs)\\
FR - Functional Requirements\\
NR - Non-functional Requirements\\
BR - Behavioural Requirements\\
PR - Performance Requirements\\ 

\section{Customer Requirements / Customer Needs}
\begin{enumerate}
\item	Safety
\begin{enumerate}
	\item	Emergency button, that shall cut-off power when pressed.
	\item	Tamper proof.
	\item	The system shall be safe to operate
\end{enumerate}
\item	Environmental
\begin{enumerate}
	\item	The system shall be used at the facility of AU-Herning. 
	\item	The system shall be placed outside.
	\item	The system-controller shall be placed inside a shed.
\end{enumerate}
\item	Usability
\begin{enumerate}
	\item	The system shall function without user interaction.
	\item	The system shall log information.
	\item	The system shall be as efficient as possible.
	\item	The system shall convert solar energy to electricity.
	\item	The system shall act as a showcase.
	\item	The system shall function without major problems for a duration of 8 years.
	\item	The system cost shall not exceed the user budget.
\end{enumerate}
\end{enumerate}
\newpage
\section{Functional Requirements}
\textit{What has to be done?}
\begin{enumerate}
\item	Usability
\begin{enumerate}
	\item	The solar panel shall follow the position of the sun.
	\item	The system shall convert solar power into electrical power.
	\item	The system shall use a data look-up table to get the correct sun position at the correct time
	\item	The system shall log information about the system
	\item	The system shall have a control panel for manual control of the solar panel
	\item	The system shall have a webpage where information can be seen.
	\item	The system shall be supplied from the light grid
\end{enumerate}
\item	Safety
\begin{enumerate}
	\item	The system shall detect if extra resistance is applied to the motors.
	\begin{enumerate}
		\item	The motors shall stop if the resistance is too high
		\end{enumerate}
	\item	The emergency button shall be red and conspicuous
	\item	Dangerous parts of electronics shall be isolated from user interaction
	\item	Dangerous moving parts shall be isolated from user interaction
	\item	The motors of the system shall be limited in movement
	\item	The system shall resist the weathers of Denmark
\end{enumerate}
\item Teacher Given
\begin{enumerate}
	\item The ARM7 must present an electrical interface through the EMC (Extern memory controller) on the LPC2478.
	\begin{enumerate}
		\item The buswidth must be configured as 16bit.
		\item The minimum necessary number of wait states shall be used.
		\item The electrical interface shall be able to handle 16bit read and write.
	\end{enumerate}
	\item The FPGA shall be implemented as host interface.
	\begin{enumerate}
		\item Capable of decoding 16 bit read and write from the LPC2478.
		\item Able to drive two or more LEDS through one or more memory mapped 16 bit registers.
		\item The implementation must contain a test-bench, containing a BFM (Bus Functional Model) capable of simulating CPU read and writes.
	\end{enumerate}
\end{enumerate}
\end{enumerate}

\section{Non- Functional}
\textit{Judge the operation of the system. }
\begin{enumerate}
\item	Usability
\begin{enumerate}
	\item	The system shall log input and output of the regulator, motor position and sun position
	\item 	The physical control board shall be placed inside a shed
	\item	A manual control panel shall be implemented
\end{enumerate}
\item	Safety
\begin{enumerate}
	\item	Emergency buttons shall be implemented.
	\begin{enumerate}
		\item	One shall be placed on the motor / solar panel
		\item	One shall be placed on the system-controller
		\item	The emergency buttons shall be visible from at least 5 meters away
	\end{enumerate}
	\item	A current sensor shall be implemented to measure the resistance of the motors.
	\item	The system shall follow the CE mark requirements
\end{enumerate}
\item	Environmental
\begin{enumerate}
	\item	The system shall be placed in a place with the most sun hours possible to increase efficiency
\end{enumerate}

\item Teacher given
\begin{enumerate}
	\item Each team shall write a small module design, before implementation.
	\begin{enumerate}
		\item The module design shall be approved during timebox-deployment, BEFORE implementation begins.
	\end{enumerate}
	\item Your VHDL design shall be implemented in following files:
	\begin{enumerate}
		\item name.vhd containing the RTL implementation.
		\item tb\_name.vhd containing a testbench for your module(s) above.
		\item name.uch containing the user constrains for your FPGA implementation.
	\end{enumerate}
	\item You must implement one or more IP cores in the FPGA, capable of performing system critical tasks, suitable for implementing as HWW.
	\item you shall implement uClinux driver(s) for the IP above.
	\begin{enumerate}
		\item The drivers must be implemented as a kernelspace loadable driver.
		\item Acess to the driver shall be from within a userspace program.
		\item The kernel driver and userspace program must be automatically loaded upon start of the RTOS.
		\item Your software package shall contain, as minimum, the following files
		\begin{enumerate}
			\item A makefile for the kernel module.
			\item A makefile for the userspace program.
			\item Necessary header (.h) and implementation files (.c) for the modules.
			\item Correct or create the necessary files required to load the above modules during boot.
		\end{enumerate}
	\end{enumerate}
	\item a "low level" prototype, implemented without RTOS, must be deployed and approved (preferably before the uClinux driver is created).
	\item Bus plots and measurements, performed on the Agilent 1692A logicanalyzer, must be used as a basis for the analysis and design.
	
	
	\item Relay server
	\begin{enumerate}
		\item Able to accept multiple telnet connections
		\begin{enumerate}
			\item Shall accept both tcp and upd connections
			\item Shall be able to connect to the daemon on the target
			\item Shall relay traffic unmodified between the telnet client and the daemon
		\end{enumerate}
	\end{enumerate}
	
	
	\item Daemon
	\begin{enumerate}
	\item Shall accept one tcp connection
		\begin{enumerate}
			\item Shall transfer the received data to the HW-interface' driver
			\item Shall transfer data from the HW to the client
		\end{enumerate}
	\end{enumerate}
	
	
	
	\item Driver
	\begin{enumerate}
		\item Shall offer a standard interface in /dev
		\begin{enumerate}
			\item Shall implement open, close, ioctrl, read and write
		\end{enumerate}
		\item Shall accept interrupts from HW
	\end{enumerate}
	
	
	
\end{enumerate}
\end{enumerate}


\section{Behavioural Requirements}
\textit{What to do when an action occurs.}
\begin{enumerate}
\item	Usability 
\begin{enumerate}
	\item	The motors shall turn the solar panel when the sun changes position
\end{enumerate}
\item	Safety
\begin{enumerate}
	\item	The emergency button shall cut the main power.
	\item	The motors shall stop if the resistance applied to them is higher than normal.
	\begin{enumerate}
		\item	The motor shall retry to obtain the right position after 10 seconds of it failing due to high resistance.
		\item	A red LED will be turned on after the system has tried to obtain the right position and failed twice
	\end{enumerate}
	\item	The system shall inform the user of any error through the web page.
\end{enumerate}
\item	Communication
\begin{enumerate}
	\item	When a ping is received from the Energy Hub, the system shall answer.
	\item	The system shall check if a ping isn't received
	\begin{enumerate}
		\item	If a ping isn't received the system shall shut down and inform the user
	\end{enumerate}
	\item	The system shall deactivate automatic control of the solar panel and enter manual control when a button on the psychical control board is pressed
\end{enumerate}
\item Teacher given
\begin{enumerate}
	\item Relay Server
	\begin{enumerate}
		\item Handling more than one connection
		\begin{enumerate}
			\item If more than one active let the others wait - give a message
			\item When a blocking connection is terminated the next waiting connection shall be connected to the daemon
		\end{enumerate}
	\end{enumerate}
	\item Daemon
	\begin{enumerate}
		\item Shall start at system start
	\end{enumerate}
	\item Driver
	\begin{enumerate}
		\item Interrupt handling
		\begin{enumerate}
			\item When interrupted the state of the HW shall be made ready on the read interface
		\end{enumerate}
	\end{enumerate}
	
\end{enumerate}



\end{enumerate}

\section{Performance Requirements}
\textit{How well does the system do? (Judge the Functional Requirements )}
\begin{enumerate}
\item	Usability
\begin{enumerate}
	\item	The solar panel shall not face more than [10\%] in the wrong direction of the sun
\end{enumerate}
\item	Safety
\begin{enumerate}
	\item	The resistance of the motors shall not exceed [10\%] of normal.
	\item	The emergency button shall cut the power within [X] seconds
	\item	The emergency button shall have diameter of 40mm
	\item	The motors stop if the resistance exceed [X\%] of normal
	\begin{enumerate}
		\item	The motor shall stop trying to obtain the correct position after 2 tries.
		\end{enumerate}
	\item	The horizontal part of the motor of the system shall only be able to turn from east to west (180 degrees)
	\item	The vertical part of the motor of the system shall be able to turn from -5 degrees to 90 degrees
	\item	The system-controller shall not exceed 1m3
\end{enumerate}
\item	Communication
\begin{enumerate}
	\item	When a ping is received, the system shall respond within 500 milliseconds.
	\begin{enumerate}
		\item	The system checks for pings every 5 second
		\item	If no ping is received the system will shut down within [X] seconds
	\end{enumerate}
	\item	The system shall reactivate automatic control of the system when no button has been pressed on the physical control board for 10 minutes.
	\item	The motors shall update their position every [X] minutes
	\item	The system shall log information every 10 seconds and send an average every minute to the hub
	\item	The system components which take more than 2 hours to switch shall have a life span of 8 years or greater
	\item	The output from the solar panel shall be regulated to 30V with a tolerance of 10\%
	\item	The system noise shall not exceed 50dB
\end{enumerate}
\item	Financial
\begin{enumerate}
	\item	The system components which are financially heavy , shall have a life span of 8 years or greater
	\item	The system costs shall not exceed [X] kroner.
\end{enumerate}
\end{enumerate}

% Bottom of the page
\end{document}