\chapter{Material and Methods (Theory)}
During this project we will use the EUDP guideline found at www.eudp.net, to give a structured method of working. During this process the problem will be analyzed and discussed through several times, before the product will be realized. This is done to understand what have to realize and how this can be done. If the problem is analyzed and a good solution is found, then the solution will be analyzed and validated if it is possible or not.
A document called “Writing reports with EUDP” created by lectures at AU- Herning will be followed, this will provide a good structure to the report, and together with the good working process structure from the EUDP method will give an overall good structure of the project and its documentation.
As mentioned before, the system has to be part of a bigger system. This part has to function and communicate with other parts, made by other teams. Communication with the other teams will be kept in order to make a common interface and to find out, how the interaction between each other’s parts will be. A webpage will be made where the user can find information about all the parts made by the different teams. A team representative from each team is chosen, whom plan and attend to meetings where all the representatives discuss the common details. Meetings will be made in order to have meetings with the teachers, to ensure that the process is going correct and smoothly. They also have to know what we are doing, so we are where we have to be to the exams. They will also advise us to make different parts and instruct us in how we could make the different parts. We can ask them if we are stuck or if we are in doubt about something. They are our guidelines.
The customers / users of the system also have to decide how they will use the system and how the interface should be. We have to satisfy their needs and make them happy. We also plan meetings with them, and we show them prototypes of our product, to ensure we are developing what they need and asked for. A lot of meetings and cooperating with the costumer has to be planned, in order to make sure the project is on right track.
It is hard to remember what is being said to all the meetings we plan, so we write summaries after every meeting; to document the words and the decisions. The class has a wiki page, where the team meetings will be uploaded, so they are available to all teams. They can be found here: LINK TO COMMON REQUIREMENTS