\chapter{Problem Statement}
The task is to make a solar panel convert the energy from the sun into a desired current / voltage value. That value is to be chosen and agreed by all teams working on the system. Different teams have to make different parts (modules) to the system, which makes green energy and stores it until it’s needed by the user. Some teams produce wind power, others solar power and some groups have to make the storing devices. One group has to make an energy hub, which will transfer the power from the gathering devices unto the storing devices.
The Solar Panel system, which is covered in this report, will convert the energy from the sun to electricity, and then transfer it to the hub. The system will gain a feature, which will track the suns position and turn the solar panel into that position, in order to gain maximum effect from the sun, thus giving us the maximal power output to the hub. There are a lot of different kinds of sun tracking systems which will provide information to help decide which system will work best for the project. The hub will communicate and request to start/stop production of power, when it need or does not need more power from our device.
The problem is that the customer needs a green energy source, which will supply the customer with energy, so he saves money over time. The cost of the system should be covered by the electricity saved by the system, after a shorter period of time.
The second problem is, that the user needs a showcase of a green energy system, which he can show to the visitors (high-school students), who is interested in green energy.
Problems:
\begin{itemize}
\item There is a need of a green energy source.
\item There is a need of a showcase system, to show for visitors.
\end{itemize}
There were different green energy sources to choose from, and we chose to construct a system, collecting energy from the sun.
Our goals are then to:

\begin{itemize}
\item Primary Goals:
\subitem Collect solar energy
\subitem energy to desired voltage/current, needed for the storage devices to work probably.
\subitem Transfer collected energy to energy hub.
\subitem Start/stop production when requested.

\item Secondary Goals:
\subitem Track the suns position and adjust position of solar panel according to the measurements.
\end{itemize}

Both the storage devices of the system and the energy hub are affected by this problem, because they need the produced energy. If this part of the system does not succeed, the modules mentioned before may not have the necessary power to work probably, so it is important to make this module work, and to make this module able to communicate and cooperate with the other modules of the system-to-be.

\section{Teacher given requirements}

Different requirements are given, to involve the different subjects in the project.

\begin{itemize}
\item system must be controlled by the LPC2478 board.
\item user interface must contain a HTML webpage.
\item from different courses must be applied to the project in suitable places (AAM, EEMB1, EEMB2, and EDSP1).
\end{itemize}